---
title: "Data Cleaning"
author: "Laura Albrecht"
date: "8/17/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

1. Load in the Colorado COVID data set using the code below.  
Note: you will need to install the readr package first. 
```{r message = FALSE, warning=FALSE}
library(readr)
colorado_covid <- read_csv("colorado_covid.csv")

```

```{r echo = FALSE, warning = FALSE, message=FALSE}
library(tidyverse)
colorado_messiest <- colorado_covid
colorado_messy <- colorado_covid %>% group_by(onset_dt , sex, age_group, `Race and ethnicity (combined)`) %>% summarise(cases = n())



colorado_clean <- separate(colorado_messy, `Race and ethnicity (combined)`, sep = ", ", into = c("race", "ethnicity"))

colorado_clean <- separate(colorado_clean, age_group, sep = " Years", into = c("age_group", NA))

colnames(colorado_clean)[1] <- "date"
```

&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  

2.  Use head() and str() to see what is in the data set.

&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  

3. In the current format, each row represents one case. This isn't very helpful for understanding and visualizing the data. Try to reformat the data and save a new data frame to recreate the following:

```{r echo = FALSE}
colorado_messy
```
&nbsp;  
&nbsp;  
Hint: The function "n()" can be used to find a group size
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  

4. The fourth column contains both race and ethnicity in one. Separate these variables into two columns called "race" and "ethnicity".

&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  



5. In the age_group column, delete the word "Years" from every row.

Hint: There are many ways you could do this. Look at the separate function or gsub function help files to find two options. 

&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
  


 

6. Change the name of the first column to "date".

&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
  
  
  


Now your data should look like this:

```{r echo=FALSE}
colorado_clean
```
  
7. Use the ggplot2 package to visualize the data in a way you think is interesting. Assign variables to color, fill, or facets to display the data in different ways.

```{r include = FALSE}
p <- colorado_covid %>% group_by(onset_dt ) %>% summarise(cases = n()) %>% ggplot(aes(x = onset_dt,y = cases))
p + geom_point()
p+geom_line()+scale_y_continuous(limits = c(0,20000))
```
```{r include = FALSE}
p <- colorado_covid %>% group_by(cdc_report_dt ) %>% summarise(cases = n()) %>% ggplot(aes(x = cdc_report_dt,y = cases))
p <- colorado_covid %>% filter(sex== "Female" | sex =="Male") %>% group_by(cdc_report_dt, sex, age_group) %>% summarise(cases = n()) %>% ggplot(aes(x = cdc_report_dt, y = cases))
p+geom_line(aes(color = sex)) + facet_wrap(~age_group)
colorado_clean$cases %>% which.max()
colorado_clean[20750,]
```

```{r include = FALSE}
colorado_covid %>% group_by(onset_dt ) %>% summarise(cases = n()) %>% filter(as.Date("2020-02-15") < onset_dt & onset_dt < as.Date("2020-07-01")) %>% ggplot(aes(onset_dt, cases))+ geom_line()
```

