---
title: "Writing Functions and Loops"
author: "Laura Albrecht"
date: "8/17/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Functions
1. Here's a function:

```{r}
f1 <- function(x) { y <- x + 1
return(y) }
```

If we replace return(y) by just y does this function do the same thing?

```{r}
f2 <- function(x) { y <- x + 1
y }
```

Pass a few values to f1() and f2() and check the results

&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;

2. Write a function that takes the relative difference between two arguments, x and y:

\begin{equation}
f(x,y) = |\frac{x - y}{y}|
\end{equation}

&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;

3. What happens when you pass x = 1 and y = 0 to the previous function? What about when you pass x = 0 and y = 0?

&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;

4. Rewrite your function so that it has a defalut value of 1 for y.

&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;

5. Add an if statment to your function so it prints an error message if y = 0.

&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;



6. Create a for loop that finds the square root of every element in the following vector:
```{r}
x <- c(2, 4, 6, 8, 10)
```

&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;

7. Add an else statement to the following code in the case that Team B wins

```{r}
team_a <- 3 # Number of goals scored by Team A
team_b <- 1 # Number of goals scored by Team B
if (team_a > team_b){
  print ("Team A wins")
}
```

&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;

8. team_a and team_b play in a best of 7 series. The scores are given in the following vectors:

```{r}
team_a <- c(4, 1, 2, 3, 1, 0, 2)
team_b <- c(0, 2, 3, 2, 0, 2, 1)
```

Write a for loop to print the name of the team that won each game.

```{r include = FALSE, echo = FALSE}
for(i in 1:7){
  if(team_a[i] < team_b[i]){
    print("Team B won")
  } else{
    print("Team A won")
  }
}

```

